%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Overleaf Link
% https://www.overleaf.com/project/600a6ebe177355bb1cfc6789

\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Pratheek}{Bhandary}{
pratheekbhandary@gmail.com |  +91-8660319312
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.25\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{NMAMIT}
\descript{BE in Electronics and Communication}
\location{June 2015 | Nitte, Karnataka}
\location{CGPA: 8.23}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
\href{https://github.com/pratheekbhandary}{\bf github.com/pratheekbhandary} \\
\href{https://www.linkedin.com/in/pratheekbhandary}{\bf linkedin.com/in/pratheekbhandary} \\
\href{https://pratheekbhandary.netlify.app/}{\bf pratheekbhandary.netlify.app} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\textbf{Over 5000 lines:}\\
JavaScript \textbullet{}React \textbullet{}Redux \textbullet{}Relay
Golang \textbullet{}SCSS \textbullet{}NodeJs \textbullet{} GraphQl
HTML5 \textbullet{} CSS3\\
\textbf{Over 1000 lines:}\\
Python \textbullet{} Next.Js \textbullet{} Docker \textbullet{} PostgreSQL 
GCP - Cloud Functions | Compute Engine | Cloud Storage \textbullet{} AWS\\
\textbf{Familiar:}\\
React-Native \textbullet{} Nginx \textbullet{} Shell
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     CERTIFICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Certifications}
\textbullet{} M101JS: MongoDB for Node.js Developers [2018]\\
\textbullet{} Java Programming [2014]
\sectionsep

\subsection{Courses}
\textbullet{} Infosys Training Programme\\
\textbullet{} Node JS: Advanced Concepts\\
\textbullet{} Modern React with Redux\\
\textbullet{} Introduction to D3.js\\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.74\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Payoda
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}
\runsubsection{Payoda Technologies}
\descript{| Software Engineer}
\runsubsection{\small{Client: Arista Networks}}
\location{April 2019 - Present | Bengaluru, KA}
\smallskip

%Project 1
\cvproject{Showtech Analyzer}
Application to analyze showtech (log files from Arista's devices), and highlight critical issues in the device. This has reduced an engineer’s MeanTimeToRespond(MTTR) which is an indicator of increased efficiency.
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Implemented file parsers in Golang to read showtech files and store them in json format, and analyzer to extract relevant data.
\item Implemented \textbf{GraphQl} queries and mutations, DB CRUD operations using SQLBoiler, a Go ORM for Postgres.
\item Developed Home page with real time updates to emulate subscriptions only when tab is active and parsing uploaded file in webworker.
\item Implemented Tasks page UI processing of showtech file using \textbf{React-Relay}, \textbf{TypeScript} and Graphql queries.
\item Implemented Topology view to illustrate network graph of the device using \textbf{D3.js} force simulation graphs and moved complex path calculation into a webworker, significantly improving the performance.
\item Implemented a Hook to update pagination states to url (Url filtering feature).
\item Currently working on hashing files in browser using WASM library to avoid uploading existing files.
\end{tightemize}
\smallskip

%Project 2
\cvproject{Queue View}
A ReactJS based CRM tool used by Technical Assistance Center engineers.
\begin{tightemize}
    \item Built drafts feature using Operational Transforms to save incremental changes on top of RTE QuillJs.
    \item Implemented cross-tab auth token invalidation, user traffic logs, and admin portal.
\end{tightemize}
\smallskip

%Project 3
\cvproject{Dev Engagements}
A NextJs based wrapper on AWS S3 bucket to upload, download, move and copy case
attachments. Also handled the deployment of the app in EC2 using pm2.
\smallskip
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Infy
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\runsubsection{Infosys}
\descript{| Technology Analyst }
\location{Aug 2015 – April 2019 | Mangaluru, KA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\cvproject{Allstate Insurance Portal}
Rebuilt the Allstate Insurance application using the latest technologies like React, Redux.
\begin{tightemize}
\item Re-wrote Reports page improving the load time, which got appreciation from the product manager.
\item Mentored and trained junior developers, collaborated with other teams and integrated components delivered by them to make it work seamlessly with our application. 
\item Created a tool to save the redux state into Indexed DB, improving the developer experience during unit tests.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Aptean
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\runsubsection{Aptean}
\descript{| Quality Assurance Intern }
\location{Feb 2015 – Aug 2015 | Bengaluru, KA}
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
% \cvproject{Ross}
% ERP application which handles food processing from raw materials in inventory to shipping of finished goods.
% \begin{tightemize}
% \item Black box testing the application to find issues, Test case creation, Regression testing.
% \item Worked on release cycles; continuous interaction with the developer as a feature was being developed, this resulted in a short developer-testing roundabout. 
% \end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Personal Projects}
\begin{tabular}{cl}

\textbf{2018} & \makecell[l]{Hotel management application that collects orders and notifies\\
the food court. \small{\textbf{Tech Stack}: React-Redux, Firebase, React-Native, Expo.}}\\

\textbf{2018} & \makecell[l]{Portal for hackathon registration with file upload feature.\\
\small{\textbf{Tech Stack}: React-Redux, Express, Typescript, MongoDB.}}\\

\textbf{2020} & \makecell[l]{Portfolio website with emphasis on using CSS and JS animations\\
deployed in netlify.\small{\textbf{Tech Stack}: React, CSS3.}}\\

\textbf{2021} & \makecell[l]{Currently working on a tool to take notes during lectures and meetings using\\ Google STT and also differentiate voices (inspired from fireflies.ai)\\ \small{\textbf{Tech Stack}: React-Relay, Golang, Google cloud sdk.}}\\
\end{tabular}

\sectionsep
\nocite{*}

\end{minipage} 
\end{document}  \documentclass[]{article}
